%-------------------------
% CV in template style adapted for Jaegun Lee
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\usepackage[T1]{fontenc}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\renewcommand*\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey}{\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.2em]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Jaegun Lee} \\ \vspace{5pt}
    \small \faEnvelope \hspace{2pt} \href{mailto:jagunlee@postech.ac.kr}{\texttt{jagunlee@postech.ac.kr}} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Pohang, South Korea} \hspace{1pt} $|$
    \hspace{1pt} \href{https://scholar.google.co.kr/citations?hl=en&user=FCnNJhUAAAAJ}{\texttt{Google Scholar}}
    \\ \vspace{-3pt}
\end{center}

%-----------RESEARCH INTERESTS-----------
\section{RESEARCH INTERESTS}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
    \textbf{Area} {: Computational Geometry and Geometric Algorithms} \\
    \textbf{Topics} {: Partitioning, covering, triangulation, and related optimization problems}
  }}
\end{itemize}

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
  {Pohang University of Science and Technology (POSTECH)}{2022 -- Present}
  {M.S./Ph.D. Integrated Program in Computer Science and Engineering}{Pohang, South Korea}
  \resumeItemListStart
    \resumeItem{Advisor: Hee-Kap Ahn}
    \resumeItem{GPA: 4.04/4.3}
  \resumeItemListEnd

\resumeSubheading
  {Pohang University of Science and Technology (POSTECH)}{2017 -- 2022}
  {B.S. in Creative IT Engineering \& Mathematics}{Pohang, South Korea}
  \resumeItemListStart
    \resumeItem{GPA: 3.81/4.3 (\textit{Cum Laude})}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{PUBLICATIONS}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Journal Articles}}{}
\resumeItemListStart
  \resumeItem{Hwi Kim, \textbf{Jaegun Lee}, Hee-Kap Ahn. \textit{Uniformly monotone partitioning of polygons}. \textit{Theoretical Computer Science}, 2024.}
  \resumeItem{Hwi Kim, \textbf{Jaegun Lee}, Hee-Kap Ahn. \textit{Rectangular Partitions of a Rectilinear Polygon}. \textit{Computational Geometry}, 2023.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Conference Papers}}{}
\resumeItemListStart
  \resumeItem{\textbf{Jaegun Lee}, Chaeyoon Chung, Hee-Kap Ahn. \textit{Bichromatic Classifications using Strips}. \textit{The 20th Scandinavian Symposium on Algorithm Theory (SWAT)}, 2026.}
  \resumeItem{\textbf{Jaegun Lee}, Seokyun Kang, Hyeonseok Lee, Hyeyun Yang, Taehoon Ahn. \textit{CG\#Hunters Approach to Central Triangulation Under Parallel Flip Operations}. \textit{The 42nd International Symposium on Computational Geometry (SoCG)}, 2026.}
  \resumeItem{Chaeyoon Chung, \textbf{Jaegun Lee}, Hee-Kap Ahn. \textit{Covering Weighted Points using Unit Squares}. \textit{The 36th International Symposium on Algorithms and Computation (ISAAC)}, 2025.}
  \resumeItem{\textbf{Jaegun Lee}, Hyojeong An, Hwi Kim, Hee-Kap Ahn. \textit{Monotone Partitions of Simple Polygons}. \textit{The 36th International Workshop on Combinatorial Algorithms (IWOCA)}, 2025.}
  \resumeItem{Taehoon Ahn, \textbf{Jaegun Lee}, Byeonguk Kang, Hwi Kim. \textit{Incremental algorithm and local search for minimum non-obtuse triangulation}. \textit{The 41st International Symposium on Computational Geometry (SoCG)}, 2025.}
  \resumeItem{Jongmin Choi, \textbf{Jaegun Lee}, Hee-Kap Ahn. \textit{Efficient k-center algorithms for planar points in convex position}. \textit{The 18th Algorithms and Data Structures Symposium (WADS)}, 2023.}
  \resumeItem{Hwi Kim, \textbf{Jaegun Lee}, Hee-Kap Ahn. \textit{Uniformly Monotone Partitioning of Polygons Revisited}. \textit{The 34th Canadian Conference on Computational Geometry (CCCG)}, 2022.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Presentations and Talks at Workshops}}{}
\resumeItemListStart
  \resumeItem{\textit{Bichromatic Classifications using Strips}. \textit{The 17th Annual Meeting of Asian Association for Algorithms and Computation (AAAC)}, 2026.}
  \resumeItem{\textit{Monotone Partitions of Simple Polygons}. \textit{The 16th Annual Meeting of Asian Association for Algorithms and Computation (AAAC)}, 2025.}
  \resumeItem{\textit{Efficient k-center algorithms for planar points in convex position}. \textit{The 23rd Japan--Korea Joint Workshop on Algorithms and Computation (WAAC)}, 2023.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SCHOLARSHIPS & AWARDS-----------
\section{AWARDS AND FELLOWSHIPS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Awards and Fellowships}}{}
\resumeItemListStart
  \resumeItem{Third Place at the CG:SHOP SoCG Competition, 2026.}
  \resumeItem{Second Place \& First Place in Junior at the CG:SHOP SoCG Competition, 2025.}
  \resumeItem{Bang Sung-Yang Graduate Fellowship, 2022.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Research and Industry Projects}}{}
\resumeItemListStart
  \resumeItem{\textbf{Auto Nesting} --- Samsung Heavy Industries, 2025--2026.}
  \resumeItem{\textbf{Slab Yard Optimization} --- POSCO DX (Team Leader), 2023--2024.}
  \resumeItem{\textbf{Software Star Lab} --- Optimal Data Structure and Algorithmic Applications in Dynamic Geometric Environment, 2022--2025.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PATENTS-----------
\section{PATENTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Patents and Applications}}{}
\resumeItemListStart
  \resumeItem{\textit{Slab Transfer System Using Virtual Slab Yard Simulator}, Hee-Kap Ahn, \textbf{Jaegun Lee}, Jae Hoon Chung, Chae Yoon Chung, Minju Song. Korean Patent (Application), No. 10-2024-0201787, 2024.}
  \resumeItem{\textit{Efficient Optimal Facility Location Determination Methods for Convex Position Demand Points}, Hee-Kap Ahn, Tae Kang Eom, Jong Min Choi, \textbf{Jae Gun Lee}. Korean Patent, No. 10-2704974, 2024.}
  \resumeItem{\textit{Efficient Optimal Facility Location Determination Methods for Convex Position Demand Points}, Hee-Kap Ahn, Tae Kang Eom, Jong Min Choi, \textbf{Jae Gun Lee}. U.S. Patent (Application), No. 18/496700, 2023.}
  \resumeItem{\textit{METHOD AND APPARATUS FOR CLASSIFYING IMAGE}, Chi Won Sung, \textbf{Jae Gun Lee}. U.S. Patent, No. 11657594, 2023.}
  \resumeItem{\textit{METHOD AND APPARATUS FOR CLASSIFYING IMAGE}, Chi Won Sung, \textbf{Jae Gun Lee}. Korean Patent, No. 1021590520000, 2020.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACADEMIC ACTIVITIES-----------
\section{ACADEMIC ACTIVITIES}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Conference Organization}}{}
\resumeItemListStart
  \resumeItem{The 26th Korea--Japan Joint Workshop on Algorithms and Computation (WAAC), 2026.}
  \resumeItem{The 25th Korean Workshop on Computational Geometry (KWCG), 2025.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Journal Reviewing}}{}
\resumeItemListStart
  \resumeItem{\textit{Computational Geometry: Theory and Applications (CGTA)}, 2024.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Conference Reviewing}}{}
\resumeItemListStart
  \resumeItem{Symposium on Theoretical Aspects of Computer Science (STACS), 2025.}
  \resumeItem{International Conference and Workshop on Algorithms and Computation (WALCOM), 2025.}
  \resumeItem{International Symposium on Computational Geometry (SoCG), 2024.}
  \resumeItem{Theory and Applications of Models of Computation (TAMC), 2024.}
  \resumeItem{International Symposium on Algorithms and Computation (ISAAC), 2023.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATIONAL ACTIVITIES-----------
\section{EDUCATIONAL ACTIVITIES}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Teaching Assistant of AI Education Programs for Business}}{}
\resumeItemListStart
  \resumeItem{POSCO AI Expert, 2022.}
  \resumeItem{Youth AI$\cdot$Bigdata Academy, 2022.6, 2022.12, 2023, 2024.2, 2024.8, 2025.4.}
  \resumeItem{HuStar Innovation Academy\footnote{Education program of local governments (Daegu and Gyeongsangbuk-do).}, 2022.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Teaching Assistant at POSTECH}}{}
\resumeItemListStart
  \resumeItem{CSED331 Algorithms, 2022, 2023.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Teaching Assistant at Pohang Jecheol High School}}{}
\resumeItemListStart
  \resumeItem{Advanced Thinking Program, 2022.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXTRA ACTIVITIES-----------
\section{PROFESSIONAL AND OTHER ACTIVITIES}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Lab Activities}}{}
\resumeItemListStart
  \resumeItem{KWCG 2025 Local Organizer, 2025.}
  \resumeItem{Lab Manager, 2025--2026.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Work Experience}}{}
\resumeItemListStart
  \resumeItem{\textbf{Polaris3D}, 2019--2020. Developer for an out-of-stock detection model; demo at CES 2020.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Student Organization Activities}}{}
\resumeItemListStart
  \resumeItem{Student Council of the Department, 2018.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Club Activities}}{}
\resumeItemListStart
  \resumeItem{Adlib (drama club), 2017--2022; President, 2019.}
  \resumeItem{Tachyons (baseball club), 2017--Present.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
